---
title: "Analysis Double"
author: "Rutuja"
date: "2024-04-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import statements

```{r}
library(tidyverse)
```

Required keys

```{r}
chr_names<-c("chrI","chrII","chrIII","chrIV","chrV","chrVI","chrVII","chrVIII", "chrIX","chrX","chrXI","chrXII","chrXIII","chrXIV","chrXV","chrXVI")

chr_names2<-c("chr01","chr02","chr03","chr04","chr05","chr06","chr07","chr08","chr09","chr10","chr11","chr12","chr13","chr14","chr15","chr16")
```

# Reading in files

```{r}
# power to detect mutations
power<-read.delim("power_by_site_with_bases.txt",h=F)
names(power)<-c("chr","pos","hap.wt","hap.del","dip.wt","dip.del","ref")
power$chr_num<-sapply(power$chr,function(i){which(chr_names2==i)})
d <- power %>% select(chr_num, pos, ref, hap.wt, hap.del, dip.wt, dip.del)
d$pwr.tot<-rowSums(d[,c(4:7)])
```

```{r}
net <- read.csv("net_mapped/double_net.csv")
```

```{r}
df.plus <- net[net$strand == "+",]
df.minus <- net[net$strand == "-",]

d <- d %>% left_join(df.minus[,c("pos", "chr_num", "total", "feature")], by=c('pos', 'chr_num'), suffix = c("", ".minus"))
d <- d %>% rename("net_tot.minus" = "total",
                            "class.minus" = "feature")
d <- d %>% left_join(df.plus[,c("pos", "chr_num", "total", "feature")], by=c('pos', 'chr_num'), suffix = c("", ".plus"))
d <- d %>% rename("net_tot.plus" = "total",
                            "class.plus" = "feature")

d$pos500 <- ((d$pos-1) %/% 1000) * 1000 + 501
```


Starting with the replication dynamics data first

```{r}
rep.dynamics <- read.csv("replication_data/clean_rep.csv")
```

```{r}
d <- d %>% left_join(rep.dynamics[,c("pos","chr_num", "ratio", "rep.slope", "rep.sign")], by=c("chr_num", "pos500"="pos"))
```

# Now combining mutation data

Reading in the mutation data

```{r}
mut <- load("mutation_data/Sharp_etal_variants")
```

Filter to keep specific columns

```{r}
test.rv <- rv %>% select(CHROM, POS, REF, ALT, TYPE, RDH, MAT, ploidy, allele.freq, chr_copy_num, aneu11, indel.type, genic, mut.type, NCALLED)

test.rv$chr_num <- sapply(test.rv$CHROM,function(i){which(chr_names2==i)})
test.rv <- test.rv %>% rename("pos" = "POS")
```

Final join

```{r}
d <- d %>% left_join(test.rv, by = c("chr_num", "pos"))
```

# Generating more useful calculated columns

```{r}
d$net_tot.minus <- d$net_tot.minus %>% replace_na(0)
d$net_tot.plus <- d$net_tot.plus %>% replace_na(0)
d$net_tot <- d$net_tot.minus + d$net_tot.plus
d <- d %>% mutate(tr.or.not = case_when(
  !is.na(class.minus) | !is.na(class.plus) ~ TRUE,
  TRUE ~ FALSE
))

d <- d %>% mutate(class = case_when(
  !is.na(class.minus) & is.na(class.plus) ~ class.minus,
  is.na(class.minus) & !is.na(class.plus) ~ class.plus,
  !is.na(class.minus) & !is.na(class.plus) ~ "both",
  TRUE ~ "none"
))

d <- d %>% mutate(transcribed = ifelse(d$net_tot > 0, TRUE, FALSE))

df <- d
rm(d)

df <- df %>% select(-CHROM)
df$net_tot.minus <- replace_na(df$net_tot.minus, 0)
df$net_tot.plus <- replace_na(df$net_tot.plus, 0)
df$class.minus <- replace_na(df$class.minus, "none")
df$class.plus <- replace_na(df$class.plus, "none")
df$net_tot.minus <- replace_na(df$net_tot.minus, 0)
df$net_tot.plus <- replace_na(df$net_tot.plus, 0)
df$allele.freq <- replace_na(df$allele.freq, 0)
df$genic <- replace_na(df$genic, FALSE)
df$NCALLED <- replace_na(df$NCALLED, 0)
df <- df %>% mutate(mutated = ifelse(df$NCALLED > 0, 1, 0))
df$rep.strand <- df$rep.sign

ready.cols <- sapply(df, function(x)all(!is.na(x)))
ready.cols[ready.cols]
```

Adding some collision info here

```{r}
collisions <- df %>% select(chr_num, pos, rep.strand, net_tot.minus, net_tot.plus, mutated)
```

So for the transcription direction, I am using the direction of whatever is greater between net_tot.plus and net_tot.minus. Finding all the collisions spots.

```{r}
collisions <- collisions %>% mutate(tr.strand = case_when(
  net_tot.minus > net_tot.plus ~ -1,
  net_tot.plus > net_tot.minus ~ 1,
  TRUE ~ 0
))

collisions <- collisions %>% mutate(collision = case_when(
  rep.strand * tr.strand == 1 ~ 1,
  TRUE ~ 0
))

collisions <- collisions %>% mutate(net_tot = net_tot.minus + net_tot.minus)

collisions$class <- df$class
collisions <- collisions %>% mutate(ORF = ifelse(class == "ORF" | class == "ORFs", 1, 0))
collisions <- collisions %>% mutate(CDS = ifelse(class == "CDS", 1, 0))

collisions$ORF.scaled = scale(collisions$ORF)
collisions$CDS.scaled = scale(collisions$CDS)

collisions$type <- df$TYPE

collisions <- collisions %>% mutate(SNM = ifelse(type == "SNP", 1, 0))
collisions$SNM <- replace_na(collisions$SNM,0)
collisions <- collisions %>% mutate(INDEL = ifelse(type == "INDEL", 1, 0))
collisions$INDEL <- replace_na(collisions$INDEL, 0)

collisions$ref <- df$ref
collisions$rep.ratio <- df$ratio

collisions$rep.ratio <- replace_na(collisions$rep.ratio, 1)
collisions$rep.ratio.scaled <- scale(collisions$rep.ratio)
collisions <- collisions %>% mutate(ref.type = case_when(
  ref == "A" | ref == "T" ~ "A/T",
  ref == "G" | ref == "C" ~ "G/C",
  TRUE ~ NA
))
```

Trying to make a large model and working my way backwards. Making another testing dataframe

```{r}
test.df <- collisions[,c("chr_num", "pos", "rep.strand", "mutated", "collision", "net_tot", "rep.ratio", "CDS", "SNM", "INDEL", "ref.type")]
test.df$pwr.tot <- df$pwr.tot
test.df$rep.slope <- df$rep.slope
```

Making a scaled dataset

```{r}
df.scaled <- test.df[, c("chr_num", "pos", "mutated", "SNM", "INDEL", "ref.type", "CDS", "rep.strand")]
# df.scaled$rep.strand <- scale(test.df$rep.strand)
df.scaled$collision <- scale(test.df$collision)
df.scaled$net_tot <- scale(test.df$net_tot)
df.scaled$rep.ratio <- scale(test.df$rep.ratio)
df.scaled$rep.slope <- scale(test.df$rep.slope)
df.scaled$pwr.tot <- scale(test.df$pwr.tot)
# df.scaled$CDS <- scale(test.df$CDS)
```

Model making (yay!)

```{r}
mod <- glm(SNM ~ ref.type + collision * net_tot * CDS + rep.ratio + rep.strand, family = "binomial", df.scaled)
summary(mod)
```

Call:
glm(formula = SNM ~ ref.type + collision * net_tot * CDS + rep.ratio + 
    rep.strand, family = "binomial", data = df.scaled)

Coefficients:
                        Estimate Std. Error  z value Pr(>|z|)    
(Intercept)           -9.228e+00  3.822e-02 -241.416  < 2e-16 ***
ref.typeG/C            1.021e+00  4.782e-02   21.353  < 2e-16 ***
collision             -1.577e-03  2.342e-02   -0.067    0.946    
net_tot               -2.572e-03  1.899e-02   -0.135    0.892    
CDS                   -1.300e+02  1.122e+03   -0.116    0.908    
rep.ratio             -9.556e-02  2.407e-02   -3.970 7.17e-05 ***
rep.strand             1.281e-02  2.383e-02    0.538    0.591    
collision:net_tot     -2.145e-02  2.176e-02   -0.986    0.324    
collision:CDS         -2.897e+02  2.513e+03   -0.115    0.908    
net_tot:CDS           -6.330e+02  5.487e+03   -0.115    0.908    
collision:net_tot:CDS -1.419e+03  1.229e+04   -0.115    0.908    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

(Dispersion parameter for binomial family taken to be 1)

    Null deviance: 36561  on 11449703  degrees of freedom
Residual deviance: 36055  on 11449693  degrees of freedom
  (621622 observations deleted due to missingness)
AIC: 36077

Number of Fisher Scoring iterations: 25

```{r}
mod <- glm(SNM ~ ref.type + collision * net_tot + rep.ratio + rep.strand, family = "binomial", df.scaled)
summary(mod)
```

Call:
glm(formula = SNM ~ ref.type + collision * net_tot + rep.ratio + 
    rep.strand, family = "binomial", data = df.scaled)

Coefficients:
                   Estimate Std. Error  z value Pr(>|z|)    
(Intercept)       -9.227313   0.038187 -241.634  < 2e-16 ***
ref.typeG/C        1.021077   0.047816   21.354  < 2e-16 ***
collision          0.001813   0.023161    0.078    0.938    
net_tot           -0.001905   0.018004   -0.106    0.916    
rep.ratio         -0.095667   0.024061   -3.976 7.01e-05 ***
rep.strand         0.015695   0.023792    0.660    0.509    
collision:net_tot -0.023427   0.021798   -1.075    0.283    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

(Dispersion parameter for binomial family taken to be 1)

    Null deviance: 36561  on 11449703  degrees of freedom
Residual deviance: 36063  on 11449697  degrees of freedom
  (621622 observations deleted due to missingness)
AIC: 36077

Number of Fisher Scoring iterations: 12

```{r}
df.CDS <- df.scaled %>% filter(CDS == 1)
df.noCDS <- df.scaled %>% filter(CDS == 0)
```


```{r}
mod <- glm(SNM ~ ref.type + collision + net_tot + rep.ratio + rep.strand, family = "binomial", df.CDS)
summary(mod)
```

Call:
glm(formula = SNM ~ ref.type + collision + net_tot + rep.ratio + 
    rep.strand, family = "binomial", data = df.CDS)

Coefficients:
            Estimate Std. Error z value Pr(>|z|)    
(Intercept) -9.56269    0.69392 -13.781   <2e-16 ***
ref.typeG/C  0.90807    0.62696   1.448    0.148    
collision    0.21649    0.29465   0.735    0.463    
net_tot      0.39005    0.24775   1.574    0.115    
rep.ratio    0.07033    0.33012   0.213    0.831    
rep.strand   0.46543    0.41094   1.133    0.257    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

(Dispersion parameter for binomial family taken to be 1)

    Null deviance: 210.19  on 57067  degrees of freedom
Residual deviance: 203.16  on 57062  degrees of freedom
  (237 observations deleted due to missingness)
AIC: 215.16

Number of Fisher Scoring iterations: 12

```{r}
mod <- glm(SNM ~ ref.type + collision + net_tot + rep.ratio + rep.strand, family = "binomial", df.noCDS)
summary(mod)
```

Call:
glm(formula = SNM ~ ref.type + collision + net_tot + rep.ratio + 
    rep.strand, family = "binomial", data = df.noCDS)

Coefficients:
             Estimate Std. Error  z value Pr(>|z|)    
(Intercept) -9.231738   0.038177 -241.815  < 2e-16 ***
ref.typeG/C  1.021789   0.047956   21.307  < 2e-16 ***
collision   -0.006304   0.023043   -0.274    0.784    
net_tot     -0.005991   0.025238   -0.237    0.812    
rep.ratio   -0.096362   0.024136   -3.993 6.54e-05 ***
rep.strand   0.019169   0.023201    0.826    0.409    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

(Dispersion parameter for binomial family taken to be 1)

    Null deviance: 36350  on 11392635  degrees of freedom
Residual deviance: 35856  on 11392630  degrees of freedom
  (621385 observations deleted due to missingness)
AIC: 35868

Number of Fisher Scoring iterations: 12

```{r}
ggplot() +
  geom_line(aes(x=rep.dynamics$pos[rep.dynamics$chr_num==1], y=rep.dynamics$ratio[rep.dynamics$chr_num==4]), color='red')
# 
# ggplot() +
# #   geom_line(aes(x=rep.dynamics.dip$pos[rep.dynamics.dip$chr_num==1], y=rep.dynamics.dip$ratio[rep.dynamics.dip$chr_num==1]), color='blue') +
# #  
  # geom_line(aes(x=rep.dynamics.dip$pos[rep.dynamics.dip$chr_num==1], y=predict(loess.models.dip[[1]])), color='black')


# df %>% filter(chr_num == 1) %>% ggplot() +
#   geom_line(aes(x=pos, y=rep.slope.hap), color='red') +
#   geom_
```
